### 2017-06-09 project/report/architecture.tex
project and report

\chapter*{Project Description}
The overarching goal of this project is to design and construct a prototype of an alien surveillance system for OSNAP.  The surveillance system will analyze separately collected video on various server architectures to take advantage of larger core counts and advanced architecture features. The matrix computations associated with Kalman Filters and independent nature of tracking separate objects present excellent possibilities for parallelism.

@@

>>>>

\section{Original Description}

The overarching goal of this project is to design and construct a prototype of an alien surveillance system for OSNAP.  The surveillance system will analyze separately collected video on various server architectures to take advantage of larger core counts and advanced architecture features. The matrix computations associated with Kalman Filters and independent nature of tracking separate objects present excellent possibilities for parallelism.

@@

\begin{figure}
\includegraphics[width=\textwidth]{./arch.png}
\label{fig}
  \caption{General system architecture}
\end{figure}

In figure 1 of the system architecture, it is obvious that the main area of interest for this project is the design and implementation of the object tracking portion of the system since it is in parallel. Although sources of parallelism exist in other aspects of the system those will be left for future work. The object tracking section can be parallelized by treating individual objects separately and by utilizing vector architectures to parallelize the underlying calculations.
